---
title: "Lab 6 Comparing two means"
author: "Emily Miller"
output: github_document
---

## t-test

Researchers studying the number of electric fish species living in various parts 
of the Amazon basin were interested in whether the presence of tributaries 
affected the local number of electric fish species in the main rivers 
(Fernandes et al. 2004).

They counted the number of electric fish species above and below the entrance 
point of a major tributary at 12 different river locations.

The data is provided in your GitHub repository.

For each question below, write a sentence answering the question and show the 
code you used to come up with the answer, if applicable.

```{r}

library(tidyverse)

fish <- read_csv("chap12q19ElectricFish.csv")


fish_long <- 
  pivot_longer(fish, speciesUpstream:speciesDownstream,
               names_to = "location",
               values_to = "species") %>% 
  mutate(location = str_remove(location, c("species"))) %>% 
  print()


```


## Question A

> Test the hypothesis that the tributaries have no effect on the number of 
species of electric fish.

```{r t-test}

ttest_results <- t.test(formula = species ~ location, data = fish_long)

ttest_results

```

## Question B

> What is the difference in the mean numbers of species between areas upstream 
and downstream of a tributary? What is the 95% confidence interval of this 
difference in means?

ANSWER

The mean difference is 1.833333. The 95% confidence interval is -4.587031 to 
8.253697


## Question C

> State the assumptions that you had to make to complete parts (A) and (B). 
Create a graph to assess whether one of those assumptions was met.

```{r}
fish_long %>% 
  ggplot(aes(x=species)) +
  geom_histogram(
    aes(fill=location),
    bins=10,
    alpha = 0.5,
    position = "identity"
  ) +
  scale_fill_manual(values = c("darkorange", "cyan4"))+
  theme_minimal()
```

## Anova

Fiddler crabs are so called because males have a greatly enlarged “major” claw, 
which is used to attract females and to defend a burrow.

Darnell and Munguia (2011) recently suggested that this appendage might also act 
as a heat sink, keeping males cooler while out of the burrow on hot days.

To test this, they placed four groups of crabs into separate plastic cups and 
supplied a source of radiant heat (60-watt light bulb) from above. The four 
groups were intact male crabs, male crabs with the major claw removed; male 
crabs with the other (minor) claw removed (control); and intact female fiddler 
crabs.

They measured the body temperature of crabs every 10 minutes for 1.5 hours. 
These measurements were used to calculate a rate of heat gain for every 
individual crab in degrees C/log minute. Rates of heat gain for all crabs are 
provided in the accompanying data file.


## Question D

> Graph the distribution of body temperatures for each crab type:

```{r}
crabs <- read_csv("chap15q27FiddlerCrabFans.txt")

crabs %>% 
    ggplot(aes(x = bodyTemperature)) +
    geom_histogram(
      aes(fill = crabType), 
      bins = 8, 
      alpha = 0.5, 
      position = "identity",
      na.rm = TRUE
    ) +
    scale_fill_manual(values = c("darkorange", "red", "cyan4", "blue")) +
    theme_minimal()

```

## Question E

> Does body temperature vary among crab types? State the null and alternative 
hypothesis, conduct and ANOVA, and interpret the results.

```{r}
aov_crabs <-
  aov(bodyTemperature ~ crabType, data = crabs)
aov_crabs

summary(aov_crabs)
```

ANSWER

Null Hypothesis: There is no difference in temperature among different crab 
types.

Alternative Hypothesis: There will be a difference in temperatures among 
different crab types.

The number given from the results is smaller than 0.05, which means we reject 
the null hypothesis and fail to reject the alternative hypothesis.
